Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-16 main.tex
example VPA: new measure

Let us assume a third component in the symbols of $\Deltac$ 
which is the duration of the associated time interval.
It is used to check the timestamps in the symbols.
%
For instance, the following call transition starts in state
$q_{{i}/{c}}$, meaning that the current interval has number~$i$ 
amongst $c$ sub-intervals of duration~$\ell$ (as indicated by the stack top).
It reads a new time-division symbol~$\ccall{d}$.
The date for this symbol has to be the time $\tau$ 
for the previous time-division symbol read~$\ccall{c}$ (found on the stack)
plus the total duration of intervals read so far, $i \ell$.
The new current interval duration is~$\frac{\ell}{d}$.
%
\(
\weic\bigl(q_{{i}/{c}}, 
           \ccall{c}\ts{\tau}\ts{\ell}, q, 
           \ccall{d}\ts{\tau + i\ell}\ts{\frac{\ell}{d}}, q_{{i+1}/{c}},
           q_{{0}/{d}} \bigr) = \alpha_d
\).

\noindent
The weight of this transition is $\alpha_d$. 
We can penalize triplets compared to duplets with $\alpha_2 < \alpha_3$.
%
\noindent 
Along with $\ccall{d}$, 
the above transition pushes
the state $q_{{i+1}/{c}}$ on the stack,  
to start the next sub-interval after reading $\creturn{d}$, 
with:
\(
\weir\bigl(q_{{d}/{d}}, 
           [\ccall{d}\ts{\tau}\ts{\ell}], q_{{i}/{c}}, 
           [\,\creturn{d}\ts{\tau + d\ell}], q_{{i}/{c}} \bigr) = \one
\).

\noindent
Reading an event is done with:
\(
\weii\bigl(q_{{i}/{d}}, 
           [\ccall{d}\ts{\tau}\ts{\ell}], q_{{j}/{c}}, 
           [\mu\ts{\tau + i\ell}], q_{{i+1}/{d}} \bigr) = \alpha_\mu
\).
% cas des barres de mesure?
** case of new measure symbol: $q_0$ is a special (initial) state.
first measure:
\(
\weiec\bigl(q_0, 
           \ccall{\mathsf{m}}\ts{0}\ts{1}, q_0, 
           q_0 \bigr) = \alpha_d
\).
new measure:
\(
\weic\bigl(q_{{c}/{c}}, 
           \ccall{\mathsf{m}}\ts{\tau}\ts{1}, q_0, 
           \ccall{\mathsf{m}}\ts{\tau + 1}\ts{1}, q_0,
           q_0 \bigr) = \alpha_d
\).
\endex
\end{example}

>>>>

Let us assume a third component in the symbols of $\Deltac$ 
which is the duration of the associated time interval.
It is used to check the timestamps in the symbols.
%
For instance, the following call transition starts in state
$q_{{i}/{c}}$, meaning that the current interval has number~$i$ 
amongst $c$ sub-intervals of duration~$\ell$ (as indicated by the stack top).
It reads a new time-division symbol~$\ccall{d}$.
The date for this symbol has to be the time $\tau$ 
for the previous time-division symbol read~$\ccall{c}$ (found on the stack)
plus the total duration of intervals read so far, $i \ell$, and
the new current interval duration is~$\frac{\ell}{d}$:
%
\(
\weic\bigl(q_{{i}/{c}}, 
           \ccall{c}\ts{\tau}\ts{\ell}, q, 
           \ccall{d}\ts{\tau + i\ell}\ts{\frac{\ell}{d}}, q_{{i+1}/{c}},
           q_{{0}/{d}} \bigr) = \alpha_d
\).

\noindent
The weight of this transition is $\alpha_d$. 
We can penalize \eg triplets compared to duplets with $\alpha_2 < \alpha_3$.
%
\noindent 
Along with $\ccall{d}$, 
the above transition pushes
the state $q_{{i+1}/{c}}$ on the stack,  
to start the next sub-interval after reading $\creturn{d}$, 
with:
\(
\weir\bigl(q_{{d}/{d}}, 
           \ccall{d}\ts{\tau}\ts{\ell}, q_{{i}/{c}}, 
           \,\creturn{d}\ts{\tau + d\ell}, q_{{i}/{c}} \bigr) = \one
\).

\noindent
Reading an event is done with:
\(
\weii\bigl(q_{{i}/{d}}, 
           \ccall{d}\ts{\tau}\ts{\ell}, q_{{j}/{c}}, 
           \mu\ts{\tau + i\ell}, q_{{i+1}/{d}} \bigr) = \alpha_\mu
\).
% cas des barres de mesure?
%For the case of a new measure symbol,
%$q_{1/1}$ is a special (initial) state.
The transition for starting to read the first measure is:
\(
\weiec\bigl(q_{1/1}, 
           \ccall{\mathsf{m}}\ts{0}\ts{1}, q_{1/1}, 
           q_{1/1} \bigr) = \one
\),
and for a new measure:
\(
\weic\bigl(q_{1/1}, 
           \ccall{\mathsf{m}}\ts{\tau}\ts{1}, q_{1/1}, 
           \ccall{\mathsf{m}}\ts{\tau + 1}\ts{1}, q_{1/1},
           q_{1/1} \bigr) = \one
\).
\endex
\end{example}
